---
title: "Case Study"
output: html_document
date: "2024-10-08"
---

Load key packages and dataset.

```{r}
library(tidyverse)
library(p8105.datasets)
library(leaflet)

data(nyc_airbnb)
```

## Brainstorm questions

* Where are max and min airbnb prices?
  * What are average prices?
  * What factors affect prices?
* Where are prices going up and down over time?
* What's the relationship between number of reviews and average prices?
* Does room type affect availability? 
* What's the location of the unit? 
  * What areas are popular?
  * Popularity = number of units? Average price?
* Are there repeat hosts?
  * If so, what does that mean?
* How does price of unit change based on distance to Times Square?
* What is the relationship between minimum number of nights and reviews?
* What is the relationship between reviews and neighborhood?


```{r}
nyc_airbnb |>
  summarize (max_price = max (price))
nyc_airbnb |>
  summarize (min_price = min (price))
nyc_airbnb |>
  summarize (ave_price = mean (price))
```

```{r}
nyc_airbnb %>%
  ggplot(aes(x = price, fill = neighbourhood_group)) +
  geom_histogram() +
  facet_grid(. ~ neighbourhood_group) +
  scale_x_continuous(limits = c(0, 250))
```


```{r}
nyc_airbnb %>%
  filter(calculated_host_listings_count > 34)
```


```{r}
nyc_airbnb %>%
  group_by(neighbourhood_group) %>%
  summarise(total_reviews = sum(number_of_reviews, na.rm = TRUE)) %>%
  arrange(desc(total_reviews))
```


```{r}
nyc_airbnb |> 
  ggplot(aes(x = review_scores_location, y = price)) + 
  geom_point()
```


```{r}
nyc_airbnb |> 
  filter(neighbourhood_group == "Manhattan", 
         price < 1000) |> 
  ggplot(aes(x = lat, y = long, color = price)) + 
  geom_point(alpha = .1)
```

```{r}
nyc_airbnb |> 
  filter(neighbourhood_group == "Manhattan", 
         price < 1000, 
         room_type == "Entire home/apt") |>
  group_by(neighbourhood) |> 
  summarize(mean_price = mean(price)) |> 
  arrange(desc(mean_price))
  
```

```{r}
nyc_airbnb |> 
  filter(neighbourhood_group == "Manhattan", 
         price < 1000, 
         room_type == "Entire home/apt") |>
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) |> 
  ggplot(aes(x = neighbourhood, y = price)) + 
  geom_violin() +
  theme(axis.text = element_text(angle = 45, vjust = 1, hjust=1))
```


```{r}
pal <- colorNumeric(
  palette = "viridis",
  domain = nyc_airbnb$review_scores_location)

nyc_airbnb |> 
  filter(
    neighbourhood_group == "Manhattan", 
         price < 1000) |>
  leaflet() |> 
  addProviderTiles(providers$CartoDB.Positron) |> 
  addCircleMarkers(~lat, ~long, color = ~ pal(review_scores_location, radius = 2))
```

